Scientific Reports Title to see here (20 words or less)

### 2016-06-21 draft1.tex
Added information about barroreceptors

Olufsen and Ottesen have developed models of heart rate based on blood pressure measurements.\cite{olufsen2013practical} From the blood pressure measurement, the model predicts a firing rate for different types of receptors, which is then used to predict the response times of the parasympathetic and sympathetic nervous system.\cite{ottesen1996non} The response times are then used to predict dimensionless norepinephrine and acetylcholine concentrations, which are finally used to predict heart rate.

@@

Within the estimated parameter set, the value of $N$, the baseline firing rate increased, and both $k_1$ and $\tau_1$, representing a change in the response rate of the faster firing baroreceptors in the model.The baseline heart rate ($h_0$) decreased slightly, to 88 bpm, from the initial 100 bpm. Both $\tau_{ach}$ and $m_{ach}$, which determine how acetylcholine plays into the model, decreased dramatically in the estimated parameter set, with the reduction in $m_{ach}$ reducing the effects of a change in acetylcholine on heart rate, and the decrease in $\tau_{ach}$ increasing the rate of acetylcholine change. The estimated parameter set reduced the averaged mean squared error to 352 from 1167. As seen in Figure \ref{fig:paramscomparsionNLopt}, the estimated parameters slightly overestimate heart rate for this patient, but they perform far better than the original parameters, which severely underestimate the heart rate.

>>>>

Olufsen and Ottesen have developed models of heart rate based on blood pressure measurements.\cite{olufsen2013practical} From the blood pressure measurement, the model predicts a firing rate for different types of receptors, which is then used to predict the response times of the parasympathetic and sympathetic nervous system. The response times are then used to predict dimensionless norepinephrine and acetylcholine concentrations, which are finally used to predict heart rate.

@@

Within the estimated parameter set, the value of $N$, the baseline firing rate increased, and both $k_1$ and $\tau_1$, representing a change in the response rate of the faster firing baroreceptors in the model. Baroreceptors are generally divided into three groups, depending on their transmission speeds (on the order of half a second, five seonds, and five hundred seconds), but this model only includes two types. \cite{ottesen1996non} The increase in $\tau_1$ and the decrease in $\tau_2$ in the estimated parameter set may be the result of oversimplification.

The baseline heart rate ($h_0$) decreased slightly, to 88 bpm, from the initial 100 bpm. Both $\tau_{ach}$ and $m_{ach}$, which determine how acetylcholine plays into the model, decreased dramatically in the estimated parameter set, with the reduction in $m_{ach}$ reducing the effects of a change in acetylcholine on heart rate, and the decrease in $\tau_{ach}$ increasing the rate of acetylcholine change. The estimated parameter set reduced the averaged mean squared error to 352 from 1167. As seen in Figure \ref{fig:paramscomparsionNLopt}, the estimated parameters slightly overestimate heart rate for this patient, but they perform far better than the original parameters, which severely underestimate the heart rate. This behavior is typical of the model on patients in this study.
